---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# makeproject

<!-- badges: start -->
<!-- badges: end -->

The goal of makeproject is to quickly deploy new project folders, with a consistent architecture.

## Installation

You can install the released version of makeproject from [Github](https://github.com/nibortolum/makeproject) with:

``` r
library(devtools)
install_github("https://github.com/nibortolum/makeproject")
```

More advanced versions will be pushed to CRAN in the future.

## Example

This is a basic example which shows you how to crete a project folder:

```{r example}
library(makeproject)

## Once in the proper folder :

make_project("kickassAnalysis")
```

Do not pur white spaces in your poject name. It will be ugly and may mess up with path handling, depending on which OS youre working on.